---
title: "dsClusterAnalysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsClusterAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## About DataSHIELD

DataSHIELD is a software package for non-disclosive federated data analysis using a client - server function architecture. For further information, visit https://www.datashield.ac.uk. The most comprehensive packages - dsBaseClient and dsBase - can be found at https://github.com/datashield/dsBase and https://github.com/datashield/dsBaseClient, respectively.
The dsClusterAnalysis package together with the dsClusterAnalysisClient package (https://github.com/FlorianSchw/dsClusterAnalysisClient) provide additional functionality for DataSHIELD.


## Installation

install.packages("devtools")

library(devtools)

devtools::install_github("FlorianSchw/dsClusterAnalysis")

library(dsClusterAnalysis)




```{r setup}

```



## Acknowledgements

I am thankful for the help and support of the DataSHIELD Developer Team.


## Contact

Florian.Schwarz@dife.de






